---
format:
  pdf:
    number-sections: true
    papersize: a4
    keep-tex: false
    # thanks: 
crossref:
#  sec-prefix: OSM
  sec-labels: alpha A
citeproc: false # to make multibib and wordcount work
filters:
  - at: pre-render
    path: "_extensions/pandoc-ext/multibib/multibib.lua"
  - at: pre-render
    path: "_extensions/andrewheiss/wordcount/wordcount.lua"
validate-yaml: false # for multibib to work
  # - authors-block
# reference of multibib: https://www.andrewheiss.com/blog/2023/12/11/separate-bibliographies-quarto/
bibliography:
  main: apc_base_main.bib
  appendix: apc_base_app.bib
citation_package: natbib
tables: true # enable longtable and booktabs
fontsize: 12pt
indent: true
geometry: margin=1in
linestretch: 1.5 # double spacing using linestretch 1.5
citecolor: black
linkcolor: black
link-citations: true
execute:
  echo: false
  message: false
  warning: false
  dpi: 300
editor_options: 
  chunk_output_type: console
title: |
  | Something: An Age-Period-Cohort Analysis
abstract: |
  blah blah blah
keywords:
  - climate change
  - public opinion
editor: 
  markdown: 
    wrap: sentence
---

\pagenumbering{gobble}

# Authors {.unlisted .unnumbered}

-   Boram Min, ORCID: <https://orcid.org/XXXX-XXXX-XXXX-XXXX>, Ph.D. candidate, Department of Political Science, University of Iowa, [boram-min\@uiowa.edu](mailto:boram-min@uiowa.edu){.email} 

-   Nicole Kemmitt, ORCID: <https://orcid.org/XXXX-XXXX-XXXX-XXXX>, Ph.D. candidate, Department of Political Science, University of Iowa, [nicole-kemmitt\@uiowa.edu](mailto:nicole-kemmitt@uiowa.edu){.email}

-   Frederick Solt, ORCID: <https://orcid.org/0000-0002-3154-6132>, Professor, Department of Political Science, University of Iowa, [frederick-solt\@uiowa.edu](mailto:frederick-solt@uiowa.edu){.email}

\pagebreak

```{=tex}
\renewcommand{\baselinestretch}{1}
\selectfont
\maketitle
\renewcommand{\baselinestretch}{1.5}
\selectfont
```

```{=tex}
\begin{abstract}
blah blah blah

\textbf{Keywords:} Climate change, public opinion, China, xxx

\textbf{Word Count:} xxx
\end{abstract}

```
\pagebreak

\pagenumbering{arabic}

[intro paragraphs: importance of the question, to the discipline and the world]

```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dev = "png",
  dpi = 800,
  cache = TRUE,
  fig.width = 7,
  fig.height = 4,
  plot = function(x, options) {
    hook_plot_tex(x, options)
  }
)

if (!require(pacman)) install.packages("pacman")

library(pacman)
# load all the packages you will use below 
p_load(
  tidyverse,
  here,
  rio,
  countrycode,
  patchwork,
  ggthemes,
  ggtext,
  dotwhisker,
  vroom,
  tinytable,
  gt,
  kableExtra,
  modelsummary
) 

```

```{r define_funs}
# define functions
not_all_missing <- function(variable) {
    !all(is.na(variable))
}

standardize_country_names <- function(variable) {
    variable %>% 
        labelled::labelled(., attr(., "labels")) %>%
        labelled::to_factor(levels = "prefixed") %>%
        forcats::fct_relabel(., function(x) 
            stringr::str_remove(x, "\\[\\d+\\]\\s+")) %>%
        as.character() %>% 
        countrycode::countrycode("country.name", "country.name")
}

set.seed(324)
```

```{r wrangle_data, eval=FALSE}
eib_dir <- "../Data/dcpo_surveys/misc_files/eib_files"

eib_files <- paste0("climate_survey20", 18:24,
                    "/eib_cs20", 18:24, ".RData")

eib_ee <- map(eib_files, 
              ~ rio::import(here(eib_dir, .x),
                                       trust = TRUE) %>% 
                  filter(country == "Estonia") %>% 
    select(where(not_all_missing)))

saveRDS(eib_ee,
            here("data-raw", "eib_ee.rds"))

# I have gotten the data into a usable format in this file, and the questions can be viewed in the codebook file (`data-raw/all_cb.csv`).  The substantive questions are different in pretty much every year (except 2020 and 2021)
```

```{r load_data}
eib_ee <- readRDS(here("data-raw", "eib_ee.rds"))

# this file is a list of seven datasets; grab any one year's data by choosing it from the list like so (2024 is the seventh year):
eib2024_ee <- eib_ee[[7]]
```

# Climate Change Attitudes in Estonia

[theory: who should we expect to care more (or whatever DVs you choose) about climate change]

# Data and Method
Previously untapped survey dataset
[maybe scatterplots]

**Remember that the publication value of these data is that no one has used them yet (because they are hard to get and badly formatted when you do get them).  _Please keep the repo private, and do not circulate the data_.**

# Results
[plots not tables]

# Conclusions
[implications and importance of our answers, to the discipline and the world]

\pagebreak

# References {.unnumbered}

::: {#refs-main}
:::



\pagebreak

```{=tex}
\renewcommand{\baselinestretch}{1}
\selectfont
\maketitle
\selectfont
```
```{=tex}
\pagenumbering{arabic}
\renewcommand*{\thepage}{A\arabic{page}}
```
```{=tex}
\setcounter{section}{0}
\renewcommand*{\thesection}{A\arabic{section}}
```
```{=tex}
\setcounter{figure}{0}
\renewcommand*{\thefigure}{A\arabic{figure}}
```
```{=tex}
\setcounter{table}{0}
\renewcommand*{\thetable}{A\arabic{table}}
```
```{=tex}
\vspace{-.5in}
\begin{center}
\begin{Large}
Supplementary Material
\end{Large}
\end{center}
```


\listoftables

# Tabular Results
\clearpage

```{r}
#| label: tbl-models
#| tbl-cap: "Tabular Results"
#| cache: false


```

# References {.unnumbered}

::: {#refs-appendix}
:::





